My Cool Title

### 2019-04-30 paper.tex
Added section head
Added experiment design intro@

>>>>

To evaluate the effectiveness of our POMDP controller and guidance system, we designed a set of experiments that can measure its performance in driving a user towards a target object within the environment. 
We also conducted an additional set of experiments with an alternative guidance system to act as a baseline measurement to compare our results to and provide additional context. 
This alternative `guidance' system does not actually provide any guidance instructions to the user, instead it provides the user with the raw observation output from the object classifier and makes use of the user's intuition and prior environment knowledge to generate actions. 
The goal of both the guided and unguided experiment cases were to find an object within a static environment. 
Details on the design of these experiments are given in the next sections.

\subsection{Unguided Case}

\subsection{Guided Case}
